disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
This is kinda subtle. You often talk about predicting at the pixel level before we are even talking about estimation. I think its better to just write a model for the process, then estimate theparameters after.
Just weird to start talking about priors without stating that were doing bayes.

For the disaggregation model, we first predict the rate, $pred_i$, at pixel level:
%
\begin{equation} \label{eq:lp}
link(pred_i) = \beta_0 + \beta X + GP(s_i) + u_j
\end{equation}
%

where $\beta$ are the regression coefficients, $X$ are the covariates, $GP$ is the gaussian random field and $u_j$ is the polygon-specific iid random effect. The user defined link function is given by $link$. The Gaussian random field has a Matern covariance function, with hyperparameters $\rho = \frac{\sqrt{8\lambda}}{\kappa}$, the range of the field (beyond which correlation is $<$ 0.1), and $\sigma$, the marginal standard deviation, relating the magntiude of the variation of the field. Each of the model parameters and hyperparameters are given priors, which is discussed later.

>>>>

For the disaggregation model, we first model the rate, $pred_i$, at pixel level:
%
\begin{equation} \label{eq:lp}
link(pred_i) = \beta_0 + \beta X + GP(s_i) + u_j
\end{equation}
%

where $\beta$ are the regression coefficients, $X$ are the covariates, $GP$ is the gaussian random field and $u_j$ is the polygon-specific iid random effect. The user defined link function is given by $link$. The Gaussian random field has a Matern covariance function, with hyperparameters $\rho = \frac{\sqrt{8\lambda}}{\kappa}$, the range of the field (beyond which correlation is $<$ 0.1), and $\sigma$, the marginal standard deviation, relating the magntiude of the variation of the field. As we are working in a Bayesian setting, each of the model parameters and hyperparameters are given a prior, which is discussed later.
